Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-16 2017-EUROPAR/Gamification/paper.tex
Starting experiments

\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/login.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}

@@

\section{Experiment}
\label{sec:experiments}
In the browser, each page visiting the experiment loads an HTML Worker
that runs a local island of an evolutionary algorithm to solve a
multimodal problem called {\em l-trap}, which has been used extensively 
as a benchmark for evolutionary algorithms \cite{fernandes2009using,nijssen2003analysis}. 
This function counts the number of bits in a sequence $l$ and assigns
the local maximum $a$ if it has got 0 bits and the global maximum $b$ if it has $l$
bits. As seen in Figure \ref{fig:trap} the fitness falls into a {\em trap} 
as the number of bits is increased, decreasing linearly until a change in slope 
is reached at point $z$, adding deceptive component for evolutionary algorithms. 
To increase the difficulty trap functions can be concatenated.
In our case we have used $40$ concatenated traps. The trap function  defined as:   
\[ f(u)= 
    \begin{cases} 
      \frac{a}{z}(z-u) & \text{if } u\leq z\\
      \frac{b}{l-z} (u-z)& \text{otherwise} 
   \end{cases}
\]
\begin{figure*}[t]
    \centering
        \includegraphics[width=3in]{img/trap.png}
    \caption{Trap function.
    }
    \label{fig:trap}
\end{figure*}

@@

>>>>

@@

\section{Experiment}
\label{sec:experiments}

In order to test the kind of impact using a gamification technique has on 
user engagement in an ephemeral evolutionary system, a gamification 
technique was applied to the {\sf NodIO} volunteer computing framework 
described in \cite{DBLP:conf/gecco/MereloCGCRV16,2016arXiv160101607M}.
In this experiment users have the option to register to then login to 
the web application, using the graphical interface shown in Figure \ref{fig:login}.
After login registered users are welcomed by their name, and have
the oportunity to be listed in a leader-board.

\subsection{Setup}

\subsection{Problem}
In the browser, each page visiting the experiment loads an HTML Worker
that runs a local island of an evolutionary algorithm to solve a
multimodal problem called {\em l-trap}, which has been used extensively 
as a benchmark for evolutionary algorithms \cite{fernandes2009using,nijssen2003analysis}. 
This function counts the number of bits in a sequence $l$ and assigns
the local maximum $a$ if it has got 0 bits and the global maximum $b$ if it has $l$
bits. As seen in Figure \ref{fig:trap} the fitness falls into a {\em trap} 
as the number of bits is increased, decreasing linearly until a change in slope 
is reached at point $z$, adding deceptive component for evolutionary algorithms. 
To increase the difficulty trap functions can be concatenated.
In our case we have used $40$ concatenated traps. The trap function  defined as:   
\[ f(u)= 
    \begin{cases} 
      \frac{a}{z}(z-u) & \text{if } u\leq z\\
      \frac{b}{l-z} (u-z)& \text{otherwise} 
   \end{cases}
\]
\begin{figure*}[t]
    \centering
        \includegraphics[width=3in]{img/trap.png}
    \caption{Trap function.
    }
    \label{fig:trap}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/login.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:login}
\end{figure*}

The Gamification techinique applied to the NodIO framework
